\mytitle

### 2017-11-02 paper.tex
nits

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{ZooKeeper\xspace}
\newcommand{\libpaxos}{libPaxos\xspace}
\newcommand{\spaxos}{S-Paxos\xspace}
\newcommand{\crane}{\textsc{Crane}\xspace}

@@

\author[+]{Authors}
\maketitle
%\thispagestyle{empty}

@@

>>>>

\newcommand{\apache}{\v{Apache}\xspace}
\newcommand{\mongoose}[0]{\v{Mongoose}\xspace}
\newcommand{\ab}{\v{ApacheBench}\xspace}
\newcommand{\clamav}{\v{ClamAV}\xspace}
\newcommand{\upnp}{uPnP\xspace}
\newcommand{\mediatomb}{\v{MediaTomb}\xspace}
\newcommand{\mencoder}{\v{mencoder}\xspace}
\newcommand{\mongodb}{\v{MongoDB}\xspace}
\newcommand{\ssdb}{\v{SSDB}\xspace}
\newcommand{\mysql}{\v{MySQL}\xspace}
\newcommand{\sysbench}{\v{SysBench}\xspace}
\newcommand{\zookeeper}{ZooKeeper\xspace}
\newcommand{\libpaxos}{libPaxos\xspace}
\newcommand{\spaxos}{S-Paxos\xspace}
\newcommand{\crane}{\textsc{Crane}\xspace}
\newcommand{\dare}{DARE\xspace}

@@

\author[+]{}
\maketitle
%\thispagestyle{empty}

@@

Although there are some hardware-accelerated consensus 
protocols~\cite{consensusbox:nsdi16,netpaxos:sosr15,specpaxos:nsdi15,
nopaxos:osdi16} which are effective on reducing consensus latency, they are 
either unsuitable for general server programs or are not designed to be 
scalable on concurrent client connections. For instance, 
\dare~\cite{dare:hpdc15}, a novel consensus protocol, achieves the lowest 
consensus latency on a small number of client connections, but both its 
evaluation shows that its consensus latency increases quickly when  
more connections are added. Other recent 
works~\cite{nopaxos:osdi16,specpaxos:nsdi15,netpaxos:sosr15} 
leverage in-network serialization in a datacenter to safely skip 
consensus if packets arrive at replicas in the same order. 
These works require reconstructing a server program to use their new libraries 
for checking the order of packets, so they are not designed to run legacy 
server programs.
